Dirac neutrino mass generation from Majorana messenger

### 2019-09-07 draft.tex
Updates from Overleaf

\section{The model}
\label{sec:Model}
%
\begin{table}[t!]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline  
    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_X$ \\ \hline
    % $H $  & 2  1/2  &  0 \\
    $\eta$  & $\boldsymbol{2}$ & $1/2$  & $1$ \\
    $S$ & $\boldsymbol{1}$ & $0$  & $2$ \\
    $\sigma$ & $\boldsymbol{1}$ & $0$ & $3$ \\
    \hline
    % $Q_{L_{i}}$  & $(2,-1/6)$ & $0$ \\
    % $\overline{u_{R_{i}}}$ & $(1,-2/3)$ & $0$ \\
    % $\overline{d_{R_{i}}}$ & $(1,1/3)$ & $0$ \\
    % \hline
    % $L_i$  & $(2,-1/2)$ & $0$ \\
    % $\overline{e_{R_i}}$ & $(1,1)$ & $0$ \\
    $\nu_{Ri}$ & $\boldsymbol{1}$ & $0$ & $-4$\\
    $\nu_{R3}$ & $\boldsymbol{1}$ & $0$ & $5$\\
    $\psi_{R\alpha}$  & $\boldsymbol{1}$ & 0 & $1$ \\\hline
  \end{tabular}
  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the new $\operatorname{U}(1)_X$ gauge symmetry. }
    \label{tab:partcont}
\end{table}
%
We extend the standard model with a spontaneously broken Abelian gauge symmetry  which guarantees the total lepton number ($L$) conservation. Only the new particles including the light right handed neutrinos are charged under this symmetry. We choose the new particle set such that the following dimension six operator is genuinely realized at one-loop level
\begin{align}
  \label{eq:ld6}
  \mathcal{O}_{6D}=\frac{1}{\Lambda^2} \overline{L_i} \tilde{H} \nu_R S^2\,,
\end{align}
where $S$ is the singlet scalar field which spontaneously breaks the $\operatorname{U}(1)_X$ symmetry needed to forbid the Dirac and Majorana neutrino mass terms at tree level.

With the aim to illustrate the one-loop Dirac neutrino mass generation
we consider the particle content shown in Table \ref{tab:partcont} as
a possible realization of the effective operator $\mathcal{O}_{6D}$. Specifically, we introduce three scalar fields
$\eta, \sigma$ and $S$, where only $S$ develops a nonzero vacuum
expectation value (VEV),  a set of three singlet fermions,
$\nu_{Ri}$ ($i=1,2$) and $\nu_{R3}$, and another set of three heavy Majorana fermions, $\psi_{R\alpha}$ ($\alpha=1,2,3$).  
%The model also includes an additional $\operatorname{U}(1)_X$ gauge
%symmetry which is used to forbid the Dirac and Majorana neutrino mass
%terms at tree level.
%Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $\operatorname{SU}(2)_L$.
The $\operatorname{U}(1)_X$ charges for the new particles are defined by the anomaly cancellation conditions and the gauge invariance in Yukawa and scalar interactions.
%In this model the neutrinos are Dirac fermions. Particle content and their respective charges are show in Tab.~\ref{tab:partcont}.

@@

where $L_{i}$ and $H$ are the SM lepton and Higgs doublets, respectively,  $\widetilde{\eta} = i \sigma_2 \eta^*$, and $h$, $y$ and $\kappa$ are matrices in the flavor space. 

@@

On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis in such a way their masses are $M_{\psi_\alpha}=\sqrt{2}\kappa_{\alpha\alpha}v_S$, with $M_{\psi_1}<M_{\psi_2}<M_{\psi_3}$.
%\begin{pmatrix}
  %\psi_1 &
  %\psi_2 &
  %\psi_3
%\end{pmatrix}^{\operatorname{T}}$$

\section{Neutrinos}
\label{sec:Neutrinos}
%
\begin{figure}
\centering
\includegraphics[scale=0.75]{Neutrino_Loop.pdf}
\caption{One-loop generation of Dirac neutrino mass}
\label{fig:zee}
\end{figure}
%
 The Dirac neutrino mass matrix in this model is generated at one-loop level according to the diagram in  Fig.~\ref{fig:zee}. The expression for $\mathcal{M}_{\nu}$ is given by
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} = \frac{1}{64 \pi^{2}}  \frac{\lambda_8 v_S v_H} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} M_{\psi_{\alpha}}y^{*}_{j\alpha}\left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
\end{align}
%
%check the following formula:
where $F(x) =x \log x/(x-1)$. 
%, $M_{\psi_{a}}$ is
%the fermion mass and $\chi_{R_{(1,2)}}$ ( $\chi_{I_{(1,2)}}$ ) are the
%two CP-even (CP-odd) mass eigenstates.
It follows that to obtain nonzero neutrino masses it is necessary that $\mu\equiv\lambda_8 v_S \neq 0$. In this
way, in addition to the suppression from the seesaw mechanism, we can
have further suppression in the neutrino mass matrix for small values
of $\mu$.
The structure of the effective neutrino mass matrix is given by the
product $(M_{\nu})_{ij} \propto h_{i a} y_{a j}$, which is similar to
the structure of the neutrino mass matrix for the tree-level seesaw
mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}.

If only one
fermion $\psi_R$ is added, we will have two massless neutrinos, which
does not agree with the current data obtained from the neutrino
experiments~\cite{deSalas:2017kay}. In our case, we will assume the
existence of three fermions, generating Dirac scotogenic masses for
the two neutrinos ($\nu_{k}$ is massless due to the assignment of
charges). If we consider the case in which $m_{\eta^{\pm}}^2 = \mu^2_{\sigma} \gg \frac{1}{2} \lambda_8 v v_S$ and $\lambda_7$, $\lambda_2$, $\lambda_4 \ll 1$. Taking $m^2_{\chi_{R_{2}}}-m^2_{\chi_{R_{1}}} = \lambda_8 v v_{S}$ and $m^2_{\chi_{R_{2}}}+m^2_{\chi_{R_{1}}} = 2 m_{\eta^{\pm}}^{2}$ one finds
%
\begin{align*}
(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S v}{32 \pi^{2}} \sum_{\alpha=1}^{3} \frac{h_{i \alpha} M_{\psi_{a}}y^{*}_{j\alpha}} {m_{\eta^{\pm}}^{2}-M_{\psi_{\alpha}}^{2}} \left[1 - \frac{M_{\psi_{\alpha}}^{2}}{m_{\eta^{\pm}}^{2}-M_{\psi_{\alpha}}^{2}} \log \left( \frac{m_{\eta^{\pm}}^{2}}{M_{\psi_{\alpha}}^{2}} \right)\right]\,,
\end{align*}
%
and if we take $m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$ one has 
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} & = \frac{\lambda_8 v_S v}{32 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\eta^{\pm}}^{2}}\,, \\
& \sim 0.003~\text{eV} \left( \frac{\lambda_8}{1 \text{GeV}}\right) \left( \frac{v_{S}}{10 \text{TeV}}\right) \left( \frac{M_{\psi_{a}}}{1 \text{TeV}}\right) \left( \frac{50 \text{TeV}}{m_{\eta^{\pm}}}\right)^{2} \left( \frac{h_{i a} y_{a j}^{\dagger}}{10^{-6}}\right)\,. \nonumber
\end{align}
%
The mass matrix for Dirac neutrinos is diagonalized by
\begin{align*}
(U^{\nu}_R)^{\dagger} \mathcal{M}_{\nu} U^{\nu}_L = \mathcal{M}_{\nu}^{\text{diag}} = \text{diag}(m_1, m_2, m_3)\,,
\end{align*}
where $U^{(\nu)}_R$ and $U^{(\nu)}_L$ are unitary $3 \times 3$
matrices. The leptonic charged currents with non-massless neutrinos
are parametrized in terms of the unitary mass
\begin{align*}
U_{\text{PMNS}} = \left( U^{\ell}_L \right)^{\dagger} U^{\nu}_L\,,
\end{align*}
where is the left diagonalization matrix of the charged leptons.
As we already are in the diagonal basis after the calculation of the
one-loop neutrino masses, we can set
$U_{L}^{\ell} = \mathds{1}$. Moreover, we assume that $U_{R}^{\nu} = \mathds{1}$.
Therefore, we can express the Dirac neutrino mass matrix in the
following way
\begin{align}
(\mathcal{M}_{\nu})_{ij} = (U_{\text{PMNS}})_{ij} (\mathcal{M}_{\nu}^{\text{diag}})_{j}\,,
\end{align}
where the matrix $U_{\text{PMNS}}$ is expressed in the standard parameterization as
\begin{align*}
U_{\text{PMNS}} = \begin{pmatrix}
    1 & 0		& 0 \\
    0 & c_{23}  & s_{23} \\
    0 & -s_{23} & c_{23}
\end{pmatrix}
\begin{pmatrix}
    c_{13}  &  0 & s_{13}e^{-i\delta} \\
    0 		&  1 & 0 \\
    -s_{13}e^{i\delta} &  0 & c_{13}
\end{pmatrix}
\begin{pmatrix}
    c_{12}  & s_{12} & 0 \\
    -s_{12} & c_{12} & 0 \\
    0		& 0		 & 1
\end{pmatrix}\,,
\end{align*}
where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are neutrino mixing angles and $\delta$ is CP-violating phase.

\section{Lepton flavor violation}
\label{sec:LFV}
%
\begin{figure}
\centering
\includegraphics[scale=0.75]{LFV.pdf}
\caption{Feynman diagram for the processes $\ell_{i} \to \ell_{j} \gamma$}
\label{fig:LFV}
\end{figure}
%
The new Yukawa interactions in eq.~\eqref{eq:LagY} in our model introduce processes of charged lepton flavor violation (CLFV). These CLFV processes are induced at one loop level, as shown in the fig.~\ref{fig:LFV}. In this case, the $\overline{L} \tilde{\eta} \psi_R$ interaction allows the part of the double scalar $\eta$ ($\eta^{\pm}$) to mediate in the loop.

The most common search for CLFV focuses on the $l^{-}_{i} \to l^{-}_{j} \gamma$ process. This process is described by the effective Lagrangian
%
\begin{align}
    \mathcal{L} = \frac{\mu_{m}^{\alpha \beta}}{2} l^{-}_{\beta} \sigma^{\mu \nu} l^{-}_{\alpha} F_{\mu \nu}
\end{align}
%
where $\mu_{m}^{\alpha \beta}$ is a transition magnetic moment~\cite{Toma:2013zsa}.
The decay rate is given by~\cite{Lavoura:2003xp}
%
\begin{align}
 \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
\end{align}
%
where $t_{\alpha} = M^{2}_{\psi_{\alpha}}/M^{2}_{\eta^{-}}$ and
%
\begin{align}
    K(t_{\alpha}) = \frac{2t_{\alpha}^{2}+5t_{\alpha}-1}{12(t_{\alpha}-1)^{3}} - \frac{t_{\alpha}^{2}\log t_{\alpha}}{2(t_{\alpha}-1)^{4}}\,.
\end{align}
%
If we assume that $t_{\alpha} \to 0$, $t_{\alpha} \to 1$ and $t_{\alpha} \to \infty$, we have that $K(t_{\alpha}) = 1/12$, $K(t_{\alpha}) = 1/24$ and $K(t_{\alpha}) = 1/(6t)$, respectively.

For $i \neq j$ we have CLFV processes, these processes are severely restricted by the current bounds , which set limits to the Yukawas. The most restrictive experimental bounds is decay $\mu \to e \gamma$, which is several orders of magnitude greater than radiative decays $\tau \to~l\gamma$, with $l = e, \mu$. These restrictions are given by Br$(\mu \to e\gamma)$ \textless $5.7 \times 10^{-13} $~\cite{Adam:2013mnn}, Br$(\tau \to e\gamma) $\textless$ 3.3 \times 10^{-8}$ and Br$(\tau \to~\mu\gamma) $\textless$ 4.4 \times 10^{-8}$~\cite{Aubert:2009ag, Bona:2007qt, Miyazaki:2012mx}.

In the limit $m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$, $t_{\alpha} \to 0$ the decay width reads
%
\begin{align}
 \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} \left[ \frac{1}{12} \right] \right|^{2}\,, 
\end{align}
%
using the current experimental constraint to Br$(\mu \to e\gamma)$, can be fullfilled provided
%
\begin{align*}
    \left( \sum_{\alpha} \frac{h^{}_{i \alpha} h_{\alpha j}^{*}}{M^{2}_{\eta^{-}}} \right)^{2} \leq 5.7 \times 10^{-13} \frac{768 \pi G_{F}^{2}}{\alpha_{EM}}
\end{align*}
%
which leads to a very slight requirement,
\begin{align*}
    \left| \sum_{\alpha}h^{}_{i \alpha} h_{\alpha j}^{*}\left(\frac{50\text{TeV}}{M^{2}_{\eta^{-}}} \right)^{2} \right| \leq 12.65
\end{align*}
%
For $i = j$ we have processes that contribute to the leptonic magnetic dipole moment. In the case of the anomalous muon magnetic dipole moment, the experimental measurements does not agree with the values predicted by the SM~\cite{Lindner:2016bgg}. This can be a proof of the veracity of the model, in addition to giving restrictions on the Yukawas.

\section{Dark matter}
\label{sec:DM}
From table~\ref{tab:partcont}. we can see that after the spontaneous breaking of
$\operatorname{U}(1)_X$ there is remnant $Z_2$ symmetry under which the particles circulating the loop in fig.~\ref{fig:zee}. plus $\nu_{R3}$ are odd, while the other right handed neutrinos and the SM particles are even. The lightest odd particle can be a dark matter candidate. In this way we can have either fermionic or scalar dark matter in the model.

\subsection{Fermionic dark matter}
The relic density of DM is controlled by the $Z'$ portal~\footnote{For
  a recent review of Majorana Dark matter with a $Z'$ portal
  see~\cite{Blanco:2019hah} } and
% check Ibarra papers
also through the annihilation
$\psi_{1} \psi_{1} \to l _{\alpha}^+ \overline{l}_{\beta}^- $, via
Yukawa coupling $h^{a}_{i}$. These Yukawa couplings are restricted by
CLFV and neutrino masses. %But, Yukawa couplings $y^{a}_{j}$ is free.
In the case where the mass of the other fermions and scalars is nearly
degenerated to $\psi_{1} $, the processes of coannihilation can be
relevant for the relic density calculation~\cite{Klasen:2013jpa}.

Because the particle $\psi_{1}$ only interacts with the leptons via the Yukawa couplings, this model has no a direct detection cross section at three level.

@@

\begin{align*}
    H(T) = \sqrt{\frac{8 \pi G_{N} \rho(T)}{3}} = \sqrt{\frac{4 \pi^{3} G_{N}}{45} \left( g(T) + \frac{21}{4} \right)} T^{2}\,,
\end{align*}
%
and the $21/4$ correspond to the contribution of the right neutrinos to relativistic degrees of freedom. By finding the decoupling temperature of the right neutrinos $T^{\nu_R}_{\text{dec}} $ by a root finding method, it is possible to calculate $\Delta N_{\text{eff}}$.

>>>>

\section{The model}
\label{sec:Model}
%
\begin{table}[t!]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline  
    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_X$ \\ \hline
    % $H $  & 2  1/2  &  0 \\
    $\eta$  & $\boldsymbol{2}$ & $1/2$  & $1$ \\
    $S$ & $\boldsymbol{1}$ & $0$  & $2$ \\
    $\sigma$ & $\boldsymbol{1}$ & $0$ & $3$ \\
    \hline
    % $Q_{L_{i}}$  & $(2,-1/6)$ & $0$ \\
    % $\overline{u_{R_{i}}}$ & $(1,-2/3)$ & $0$ \\
    % $\overline{d_{R_{i}}}$ & $(1,1/3)$ & $0$ \\
    % \hline
    % $L_i$  & $(2,-1/2)$ & $0$ \\
    % $\overline{e_{R_i}}$ & $(1,1)$ & $0$ \\
    $\nu_{Ri}$ & $\boldsymbol{1}$ & $0$ & $-4$\\
    $\nu_{R3}$ & $\boldsymbol{1}$ & $0$ & $5$\\
    $\psi_{R\alpha}$  & $\boldsymbol{1}$ & 0 & $1$ \\\hline
  \end{tabular}
  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the new $\operatorname{U}(1)_X$ gauge symmetry. }
    \label{tab:partcont}
\end{table}
%
We extend the standard model with a spontaneously broken Abelian gauge symmetry  which guarantees the total lepton number ($L$) conservation. Only the new particles including the light right handed neutrinos are charged under this symmetry. We choose the new particle set such that the following dimension six operator is realized at one-loop level
\begin{align}
  \label{eq:ld6}
  \mathcal{O}_{6D}=\frac{1}{\Lambda^2} \overline{L} \tilde{H} \nu_R S^2\,,
\end{align}
where $S$ is the singlet scalar field which spontaneously breaks the $\operatorname{U}(1)_X$ symmetry needed to forbid the Dirac and Majorana neutrino mass terms at tree level.

With the aim to illustrate the one-loop Dirac neutrino mass generation
we consider the particle content shown in Table \ref{tab:partcont} as
a possible realization of the effective operator $\mathcal{O}_{6D}$. Specifically, we introduce three scalar fields
$\eta, \sigma$ and $S$, where only $S$ develops a nonzero vacuum
expectation value (VEV),  a set of three singlet fermions,
$\nu_{Rj}$ ($j=1,2$) and $\nu_{R3}$, and another set of three heavy Majorana fermions, $\psi_{R\alpha}$ ($\alpha=1,2,3$).  
%The model also includes an additional $\operatorname{U}(1)_X$ gauge
%symmetry which is used to forbid the Dirac and Majorana neutrino mass
%terms at tree level.
%Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $\operatorname{SU}(2)_L$.
The $\operatorname{U}(1)_X$ charges for the new particles are defined by the anomaly cancellation conditions and the gauge invariance in Yukawa and scalar interactions.
%In this model the neutrinos are Dirac fermions. Particle content and their respective charges are show in Tab.~\ref{tab:partcont}.

@@

where $L_{i}$ ($i=1,2,3$) and $H$ are the SM lepton and Higgs doublets, respectively,  $\widetilde{\eta} = i \sigma_2 \eta^*$, and $h$, $y$ and $\kappa$ are matrices in the flavor space. 

@@

On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis in such a way their masses are $M_{\psi_\alpha}=\kappa_{\alpha}v_S=\sqrt{2}\kappa_{\alpha\alpha}v_S$, with $M_{\psi_1}<M_{\psi_2}<M_{\psi_3}$.
%\begin{pmatrix}
  %\psi_1 &
  %\psi_2 &
  %\psi_3
%\end{pmatrix}^{\operatorname{T}}$$

\section{Neutrino masses and charged lepton flavor violation}
\label{sec:Neutrinos}
%
\begin{figure}
\centering
\includegraphics[scale=0.75]{Neutrino_Loop.pdf}
\caption{One-loop realization of the dimension-6 operator $\overline{L} \tilde{H} \nu_R S^2$ leading to Dirac neutrino masses with Majorana mediators.}
\label{fig:zee}
\end{figure}
%
Thanks to the scalar mixing term $\lambda_8$ nonzero Dirac neutrino masses are generated at one-loop level according to the diagram in  Fig.~\ref{fig:zee}. The expression for the effective neutrino mass matrix $\mathcal{M}_{\nu}$ can be cast as
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} = \frac{1}{64 \pi^{2}}  \frac{\lambda_8 v_S^2 v_H} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} \kappa_\alpha y^{*}_{j\alpha}\left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
%(\mathcal{M}_{\nu})_{ij} = \frac{1}{64 \pi^{2}}  \frac{\lambda_8 v_S v_H} %{m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} %M_{\psi_{\alpha}}y^{*}_{j\alpha}\left[ F\left( %\frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( %\frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
\end{align}
%
%check the following formula:
where $F(x) =x \log x/(x-1)$ and $M_{\psi_\alpha}=\kappa_{\alpha}v_S$ has been used once. 
%, $M_{\psi_{a}}$ is
%the fermion mass and $\chi_{R_{(1,2)}}$ ( $\chi_{I_{(1,2)}}$ ) are the
%two CP-even (CP-odd) mass eigenstates.
%It follows that to obtain nonzero neutrino masses it is necessary that $\mu\equiv\lambda_8 %v_S \neq 0$. 
Note that the structure of the effective neutrino mass matrix, given by the
product $(M_{\nu})_{ij} \propto h_{i \alpha} y_{j\alpha}$, is similar to
the structure of the neutrino mass matrix for the tree-level seesaw
mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}. 
It is also worth mentioning that if only one
fermion $\psi_R$ is added, then there will be two massless neutrinos, which
would be ruled out by the current neutrino oscillation data~\cite{deSalas:2017kay}. 
In our case, we assume the
existence of three of such fermions, generating Dirac scotogenic masses for
the two left-handed neutrinos ($\nu_{3}=\nu_{L3}+\nu_{R3}$ is massless due to the charge assignment).

In order to estimate the possible values for the parameters involved in the neutrino masses we consider the case where $\lambda_2$, $\lambda_4$, $\lambda_7 \ll 1$ and $m_\chi^2\equiv m_{\eta^{\pm}}^2 = \mu^2_{\sigma} \gg \frac{1}{2} \lambda_8 v v_S$, which leads to $a\approx b\gg c$. 
Taking into account that for the mentioned case $m^2_{\chi_{R_{2}}}-m^2_{\chi_{R_{1}}} = \lambda_8 v v_{S}$ and $m^2_{\chi_{R_{2}}}+m^2_{\chi_{R_{1}}} = 2 m^2_\chi$, we have that
%
\begin{align*}
(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S^2 v}{32 \pi^{2}} \sum_{\alpha=1}^{3} \frac{h_{i \alpha} \kappa_\alpha y^{*}_{j\alpha}} {m_\chi^{2}-M_{\psi_{\alpha}}^{2}} \left[1 - \frac{M_{\psi_{\alpha}}^{2}}{m_\chi^{2}-M_{\psi_{\alpha}}^{2}} \log \left( \frac{m_{\chi}^{2}}{M_{\psi_{\alpha}}^{2}} \right)\right]\,,
\end{align*}
%
and by furhter assuming $m_{\chi}^{2} \gg (\kappa_\alpha v_S)^2$ one finds 
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} & = \frac{\lambda_8 v_S^2 v}{32 \pi^{2}m_{\chi}^{2}} \sum_{\alpha=1}^{3} h_{i \alpha} \kappa_{\alpha}y^{*}_{j\alpha}\,, \\
& \sim 0.04~\text{eV} \left( \frac{\lambda_8}{10^{-4}}\right) \left( \frac{v_{S}}{200\,  \text{GeV}}\right)^2 \left( \frac{\kappa_\alpha}{0.5}\right) \left( \frac{2\, \text{TeV}}{m_{\chi}}\right)^{2} \left( \frac{h_{i \alpha} y_{j\alpha}}{10^{-4}}\right)\,. \nonumber
\end{align}
%
In this way, in addition to the loop suppression it is possible to 
have further suppression in the neutrino mass matrix for small values
of either $v_S$, $\lambda_8$ or $h_{i \alpha} y_{j\alpha}$.

%The mass matrix for Dirac neutrinos is diagonalized by
%\begin{align*}
%(U^{\nu}_R)^{\dagger} \mathcal{M}_{\nu} U^{\nu}_L = \mathcal{M}_{\nu}^{\text{diag}} = %\text{diag}(m_1, m_2, m_3)\,,
%\end{align*}
%where $U^{(\nu)}_R$ and $U^{(\nu)}_L$ are the unitary $3 \times 3$
%matrices associated to the right-handed and left-handed neutrino sectors. The leptonic %charged currents with non-massless neutrinos
%are parametrized in terms of the unitary mass
%\begin{align*}
%U_{\text{PMNS}} = \left( U^{\ell}_L \right)^{\dagger} U^{\nu}_L\,,
%\end{align*}
%where is the left diagonalization matrix of the charged leptons.
%As we already are in the diagonal basis after the calculation of the
%one-loop neutrino masses, we can set
%$U_{L}^{\ell} = \mathds{1}$. Moreover, we assume that $U_{R}^{\nu} = \mathds{1}$.
%Therefore, we can express the Dirac neutrino mass matrix in the
%following way
%\begin{align}
%(\mathcal{M}_{\nu})_{ij} = (U_{\text{PMNS}})_{ij} (\mathcal{M}_{\nu}^{\text{diag}})_{j}\,,
%\end{align}
%where the matrix $U_{\text{PMNS}}$ is expressed in the standard parameterization as
%\begin{align*}
%U_{\text{PMNS}} = \begin{pmatrix}
%    1 & 0		& 0 \\
%    0 & c_{23}  & s_{23} \\
%    0 & -s_{23} & c_{23}
%\end{pmatrix}
%\begin{pmatrix}
%    c_{13}  &  0 & s_{13}e^{-i\delta} \\
%    0 		&  1 & 0 \\
%    -s_{13}e^{i\delta} &  0 & c_{13}
%\end{pmatrix}
%\begin{pmatrix}
%    c_{12}  & s_{12} & 0 \\
%    -s_{12} & c_{12} & 0 \\
%    0		& 0		 & 1
%\end{pmatrix}\,,
%\end{align*}
%where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are %neutrino mixing angles and $\delta$ is CP-violating phase.

%\section{Lepton flavor violation}
%\label{sec:LFV}
%
\begin{figure}
\centering
\includegraphics[scale=0.75]{LFV.pdf}
\caption{Feynman diagram for the processes $\ell_{i} \to \ell_{j} \gamma$}
\label{fig:LFV}
\end{figure}
%
On the other hand, the $h_{i\alpha}$ Yukawa interaction in Eq.~\eqref{eq:LagY} leads to charged lepton flavor violation (CLFV) processes induced at one-loop level and mediated by the charged scalars $\eta^{\pm}$) as the ones shown in Fig.~\ref{fig:LFV} for the $\ell_i\to\ell_j\gamma$ type. 
current experimental constraint on Br$(\mu \to e\gamma)$ \textless $5.7 \times 10^{-13} $~\cite{Adam:2013mnn} and for the case $m_\chi^2=m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$
 we obtain an upper bound for the Yukawa couplings product (for a given $m_\chi$)
\begin{align}
    \left| \sum_{\alpha}h_{i \alpha} h_{j\alpha}^{*} \right| \lesssim 0.02 \left(\frac{m_\chi}{2\,\text{TeV}} \right)^{2}.
\end{align}
It is worth noticing that $y_{j\alpha}$ is not constrained by the non observation of LFV processes. 
%
%which leads to a very slight requirement,

%The most common search for CLFV focuses on the $l^{-}_{i} \to l^{-}_{j} \gamma$ process. This process is described by the effective Lagrangian
%
%\begin{align}
%    \mathcal{L} = \frac{\mu_{m}^{\alpha \beta}}{2} l^{-}_{\beta} \sigma^{\mu \nu} l^{-}_{\alpha} F_{\mu \nu}
%\end{align}
%
%where $\mu_{m}^{\alpha \beta}$ is a transition magnetic moment~\cite{Toma:2013zsa}.
%The decay rate is given by~\cite{Lavoura:2003xp}
%
%\begin{align}
% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
%\end{align}
%
%where $t_{\alpha} = M^{2}_{\psi_{\alpha}}/M^{2}_{\eta^{-}}$ and
%
%\begin{align}
%    K(t_{\alpha}) = \frac{2t_{\alpha}^{2}+5t_{\alpha}-1}{12(t_{\alpha}-1)^{3}} - %\frac{t_{\alpha}^{2}\log t_{\alpha}}{2(t_{\alpha}-1)^{4}}\,.
%\end{align}
%
%If we assume that $t_{\alpha} \to 0$, $t_{\alpha} \to 1$ and $t_{\alpha} \to \infty$, we have that $K(t_{\alpha}) = 1/12$, $K(t_{\alpha}) = 1/24$ and $K(t_{\alpha}) = 1/(6t)$, respectively.

%For $i \neq j$ we have CLFV processes, these processes are severely restricted by the current bounds , which set limits to the Yukawas. The most restrictive experimental bounds is decay $\mu \to e \gamma$, which is several orders of magnitude greater than radiative decays $\tau \to~l\gamma$, with $l = e, \mu$. These restrictions are given by Br$(\mu \to e\gamma)$ \textless $5.7 \times 10^{-13} $~\cite{Adam:2013mnn}, Br$(\tau \to e\gamma) $\textless$ 3.3 \times 10^{-8}$ and Br$(\tau \to~\mu\gamma) $\textless$ 4.4 \times 10^{-8}$~\cite{Aubert:2009ag, Bona:2007qt, Miyazaki:2012mx}.

%In the limit $m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$, $t_{\alpha} \to 0$ the decay width reads
%
%\begin{align}
% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} \left[ \frac{1}{12} \right] \right|^{2}\,, 
%\end{align}
%
%using the current experimental constraint to Br$(\mu \to e\gamma)$, can be fullfilled provided
%
%\begin{align*}
%    \left( \sum_{\alpha} \frac{h^{}_{i \alpha} h_{\alpha j}^{*}}{M^{2}_{\eta^{-}}} \right)^{2} \leq 5.7 \times 10^{-13} \frac{768 \pi G_{F}^{2}}{\alpha_{EM}}
%\end{align*}
%
%which leads to a very slight requirement,
%\begin{align*}
%    \left| \sum_{\alpha}h^{}_{i \alpha} h_{\alpha j}^{*}\left(\frac{50\text{TeV}}{M^{2}_{\eta^{-}}} \right)^{2} \right| \leq 12.65
%\end{align*}
%
%For $i = j$ we have processes that contribute to the leptonic magnetic dipole moment. In the case of the anomalous muon magnetic dipole moment, the experimental measurements does not agree with the values predicted by the SM~\cite{Lindner:2016bgg}. This can be a proof of the veracity of the model, in addition to giving restrictions on the Yukawas.

\section{Dark matter}
\label{sec:DM}
From the charge assignment presented in Table~\ref{tab:partcont} we have that a residuar $Z_2$ symmetry is left over after the $\operatorname{U}(1)_X$ symmetry breaking, with the particles circulating the one-loop neutrino mass diagram  (see Fig.~\ref{fig:zee}) and $\nu_{R3}$ being odd under it whereas $\nu_{R1}, \nu_{R2}$ and and all the SM particles are even. Thus the lightest neutral $Z_2$-odd particle can be a dark matter candidate. In other words, this model features either fermion ($\psi_1$) or scalar ($\chi_{1R}$ or $\chi_{1I}$) dark matter\footnote{Note that $Z'$ is not stable because the $Z'\to\bar{\nu}_{R3}\nu_{R3}$ decay channel can not be kinematically closed.}.

\subsection{Fermion dark matter}
Since $\psi_{R1}$ is a singlet under the SM gauge group its thermal relic density is controlled by the Yukawa and $\operatorname{U}(1)_X$ gauge interactions. 
The scenario where $\psi_{R1}$ is self annihilating through $h_{i\alpha}$ interaction resembles the very well known scotogenic model \cite{Ma:2006km} whereas for dominant gauge interactions we have the  Majorana Dark matter with a $Z'$ portal.

%$Z'$ portal~\footnote{For a recent review of Majorana Dark matter with a $Z'$ portal see~\cite{Blanco:2019hah} }
% check Ibarra papers
%also through the annihilation
%$\psi_{1} \psi_{1} \to l _{\alpha}^+ \overline{l}_{\beta}^- $, via
%Yukawa coupling $h^{a}_{i}$. These Yukawa couplings are restricted by
%CLFV and neutrino masses. %But, Yukawa couplings $y^{a}_{j}$ is free.
%In the case where the mass of the other fermions and scalars is nearly
%degenerated to $\psi_{1} $, the processes of coannihilation can be
%relevant for the relic density calculation~\cite{Klasen:2013jpa}.

%   Because the particle $\psi_{1}$ only interacts with the leptons via the Yukawa couplings, this model has no a direct detection cross section at three level.

@@
